Merging Datasets Through Deep learning

### 2018-08-31 paper2018/datasets.tex
datasets added

\section{Benchmarks}
\label{datasets}
Our benchmarks were derived from Wikidata.  Specifically, we used the \textit{also known as} property from Wikidata to get alternate forms for the same entity name for people as well as companies.  For company names, we augmented the names and surface forms in Wikidata with data from the SEC \footnote{\url{https://www.sec.gov/dera/data/financial-statement-and-notes-data-set.html}}, which has former and more recent names for companies.  There were 213106 names for people from the specific dump we extracted, and 70946 names for companies.  The extracted files and the cleansing code are available on our repository. The extracted files however contained noise that we cleaned up programmatically.  We describe the clean up rules for people and for companies separately because they were somewhat different.  In the case of people's names, we also augmented the data so the system could learn some common rules that define variants of a person's name.  This was not possible for company names.

@@

The data was then split with a 60-20-20 ratio to provide training, validation and test data respectively.  Each run was conducted with a different random split to ensure generalization of results.

>>>>

\section{Benchmarks}
\label{datasets}
Our benchmarks were derived from Wikidata.  Specifically, we used the \textit{also known as} property from Wikidata to get alternate forms for the same entity name for people as well as companies.  For company names, we augmented the names and surface forms in Wikidata with data from the SEC \footnote{\url{https://www.sec.gov/dera/data/financial-statement-and-notes-data-set.html}}, which has former and more recent names for companies.  There were 213106 names for people from the specific dump we extracted, and 70946 names for companies.  The extracted files and the cleansing code are available on our repository. The extracted files however contained significant noise that we cleaned up programmatically.  We describe the clean up rules for people and for companies separately because they were somewhat different.  In the case of people's names, we also augmented the data so the system could learn some common rules that define variants of a person's name.  This was not possible for company names.

@@

After cleansing, if a name had no alternate surface forms, they were dropped.  This resulted in 40555 company names with an average of 2.2 names each, and 195422 people's names with an average of 4.69 names each.  Using the triplet selection algorithm we created a set of 10.9 million and 1.04 million triplets for people and companies at training.  The data was then split with a 60-20-20 ratio to provide training, validation and test data respectively.  Each run was conducted with a different random split to ensure generalization of results.

\subsection{Dataset characteristics}
As a baseline, we measured how the anchors, positives and negatives were laid out in vector space based on character embeddings alone.  This gives us a measure of how difficult the problem is for the neural network to learn.  We indexed all the vector embeddings (regardless of test or train) into a nearest neighbors algorithm using the Spotify ANNOY\footnote{\url{https://github.com/spotify/annoy}} implementation.  We then queried the index for the $k$ nearest neighbors of this set, varying $k$ so it was either 20, 100, 500, or 1500 neighbors.  Our primary interest was in recall rates of positives prior to any training, to establish the baseline prior to training.  We also measured the nature of hard negatives as we varied the neighborhoods; i.e., what is the mean distance of negatives from the anchor while we increased neighborhoods, compared to the positive distances.  Figure \ref{people_characteristics} shows the results for the people data.  First, recall rate of positives in the nearest neighbor set was very low at 3\%, and it increased only to 6\%.  The difficulty of the problem for reconciling people's names is further highlighted by the distance data.  The mean distance of positives from anchor was 9.05, with a standard deviation of 3.08.  The mean distances of negatives from anchor was 2.73, with a standard deviation of 0.99 for $k$ of 20.  However even for $k$ of 1500, the mean negative distance was 3.64, well below the mean positive distance of 9.05.  The company data show a similar trend, although companies seems to be an easier problem than reconciling people data, as shown in Figure \ref{company_characteristics}.  Recall rate for companies starts at 16\% for a neighborhood size of 20, and is up to 25\% for a neighborhood size of 1500.  Mean negative distance is at 3.05 compared to 4.64 at a neighborhood size of 20, with a standard deviation of 1.44.  At a neighborhood size of 1500, mean negative sizes are slightly higher at 3.86.

\begin{figure*}[htb]
    \centering
    \begin{subfigure}[t]{0.5\textwidth}
        \centering
        \includegraphics[width=.9\linewidth]{people_recall}
        \caption{Recall rate as a function of neighborhood size}
        \label{people_recall}
    \end{subfigure}%
    ~ 
    \begin{subfigure}[t]{0.5\textwidth}
        \centering 
        \includegraphics[width=.9\linewidth]{people_distances}
        \caption{Mean negative distance from anchor as a function of neighborhood size}
        \label{modified_loss}
    \end{subfigure}
    \label{people_distances}
    \caption{Characteristics of people data}
\label{people_characteristics}
\end{figure*}

\begin{figure*}[htb]
    \centering
    \begin{subfigure}[t]{0.5\textwidth}
        \centering
        \includegraphics[width=.9\linewidth]{company_recall}
        \caption{Recall rate as a function of neighborhood size}
        \label{company_recall}
    \end{subfigure}%                                                                                                   
    ~
    \begin{subfigure}[t]{0.5\textwidth}
        \centering
        \includegraphics[width=.9\linewidth]{company_distances}
        \caption{Mean negative distance from anchor as a function of neighborhood size}
        \label{modified_loss}
    \end{subfigure}
    \label{company_distances}
    \caption{Characteristics of company data}
\label{company_characteristics}
\end{figure*}
